---
title: "Summarize the change of the human stressors over time across Belize & its Coastal Planning Units"
author: "Jade Delevaux"
created: October 2022
output:
  html_document:
    df_print: paged
---

To run this script, install the packages below

```{r Install packages needed for this script}
library(sf)
library(foreign)
library(raster)
library(rgdal)
library(dplyr)
library(exactextractr)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(rgeos)
library(sp)
library(ggpubr)
library(tigris)
library(maptools)
library(reshape)
```

Note: The current working directory (WD) is set to my local drive. Use the function "Find and replace" in R studio to replace the root of the working directory by your local path (e.g., "E:/GreenFin") to apply this script. 

To calculate the change in area of each human stressors over three timelines (2016, 2020, and 2025), we need the Coastal Planning Unit shapefile and the shapefile of each human stressor per timeline. 

## 1/ Agriculture runoff:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/agric_runoff"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of agriculture runoff}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/s0_agric_runoff.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Runoff"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "agri_tss_2016_km2" 
names(stressors_area_2016)[5] <- "agri_tss_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/agric_runoff", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of agriculture runoff}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/s1_agric_runoff.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Runoff"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "agri_tss_2020_km2" 
names(stressors_area_2020)[5] <- "agri_tss_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/agric_runoff", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of agriculture runoff}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/s2_agric_runoff.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Runoff"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "agri_tss_2025_km2" 
names(stressors_area_2025)[5] <- "agri_tss_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/agric_runoff", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate agriculture runoff change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$agri_tss_2020_km2 - stressors_area_all$agri_tss_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$agri_tss_2025_km2 - stressors_area_all$agri_tss_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_agric_runoff.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_agric_runoff_delta.csv")), row.names = F)
```

## 2/ Aquaculture:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/aquaculture"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of aquaculture}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/s0_aquaculture.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Aquaculture"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "aqua_2016_km2" 
names(stressors_area_2016)[5] <- "aqua_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/aquaculture", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of aquaculture}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/s1_aquaculture.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Aquaculture"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "aqua_2020_km2" 
names(stressors_area_2020)[5] <- "aqua_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/aquaculture", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of aquaculture}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/s2_aquaculture.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Aquaculture"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "aqua_2025_km2" 
names(stressors_area_2025)[5] <- "aqua_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/aquaculture", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate aquaculture change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$aqua_2020_km2 - stressors_area_all$aqua_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$aqua_2025_km2 - stressors_area_all$aqua_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_aquaculture.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_aquaculture_delta.csv")), row.names = F)
```

## 3/ Coastal development:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/development"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of development}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/s0_development.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Development"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "dvmt_2016_km2" 
names(stressors_area_2016)[5] <- "dvmt_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/development", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of development}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/s1_development.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Development"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "dvmt_2020_km2" 
names(stressors_area_2020)[5] <- "dvmt_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/development", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of development}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/s2_development.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Development"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "dvmt_2025_km2" 
names(stressors_area_2025)[5] <- "dvmt_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/development", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate development change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$dvmt_2020_km2 - stressors_area_all$dvmt_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$dvmt_2025_km2 - stressors_area_all$dvmt_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_development.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_development_delta.csv")), row.names = F)
```

## 4/ Dredging:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/dredging"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of dredging}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/s0_dredging.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Dredging"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "dred_2016_km2" 
names(stressors_area_2016)[5] <- "dred_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/dredging", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of dredging}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/s1_dredging.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Dredging"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "dred_2020_km2" 
names(stressors_area_2020)[5] <- "dred_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/dredging", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of dredging}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/s2_dredging.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Dredging"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "dred_2025_km2" 
names(stressors_area_2025)[5] <- "dred_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/dredging", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate dredging change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$dred_2020_km2 - stressors_area_all$dred_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$dred_2025_km2 - stressors_area_all$dred_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_dredging.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_dredging_delta.csv")), row.names = F)
```

## 5/ Fishing:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/fishing"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of fishing}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/s0_fishing.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Fishing"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "fish_2016_km2" 
names(stressors_area_2016)[5] <- "fish_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/fishing", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of fishing}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/s1_fishing.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Fishing"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "fish_2020_km2" 
names(stressors_area_2020)[5] <- "fish_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/fishing", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of fishing}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/s2_fishing.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Fishing"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "fish_2025_km2" 
names(stressors_area_2025)[5] <- "fish_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/fishing", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate fishing change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$fish_2020_km2 - stressors_area_all$fish_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$fish_2025_km2 - stressors_area_all$fish_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_fishing.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_fishing_delta.csv")), row.names = F)
```

## 6/ Oil Exploration:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/oil"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of oil}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/s0_oil.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Oil"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "oil_2016_km2" 
names(stressors_area_2016)[5] <- "oil_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/oil", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of oil}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/s1_oil.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Oil"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "oil_2020_km2" 
names(stressors_area_2020)[5] <- "oil_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/oil", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of oil}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/s2_oil.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Oil"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "oil_2025_km2" 
names(stressors_area_2025)[5] <- "oil_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/oil", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate oil change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$oil_2020_km2 - stressors_area_all$oil_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$oil_2025_km2 - stressors_area_all$oil_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_oil.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_oil_delta.csv")), row.names = F)
```

## 7/ Marine recreation:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/recreation"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of recreation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/s0_recreation.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Recreation"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "rec_2016_km2" 
names(stressors_area_2016)[5] <- "rec_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/recreation", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of recreation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/s1_recreation.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Recreation"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "rec_2020_km2" 
names(stressors_area_2020)[5] <- "rec_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/recreation", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of recreation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/s2_recreation.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Recreation"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "rec_2025_km2" 
names(stressors_area_2025)[5] <- "rec_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/recreation", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate recreation change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$rec_2020_km2 - stressors_area_all$rec_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$rec_2025_km2 - stressors_area_all$rec_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_recreation.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_recreation_delta.csv")), row.names = F)
```

## 8/ Marine transportation:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/transportation"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of transportation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/s0_transportation.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Transportation"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "trans_2016_km2" 
names(stressors_area_2016)[5] <- "trans_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/transportation", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of transportation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/s1_transportation.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Transportation"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "trans_2020_km2" 
names(stressors_area_2020)[5] <- "trans_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/transportation", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of transportation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/s2_transportation.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Transportation"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "trans_2025_km2" 
names(stressors_area_2025)[5] <- "trans_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/transportation", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate transportation change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$trans_2020_km2 - stressors_area_all$trans_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$trans_2025_km2 - stressors_area_all$trans_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_transportation.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_transportation_delta.csv")), row.names = F)
```

## 9/ Conservation:
Create a directory to save all the outputs for this timeline
```{r Create directory}
dir.create(file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/conservation"), showWarning=TRUE, recursive=TRUE)
```

Import the shapefile with the CPU boundaries
```{r Import the coastal planning units shapefile}
cpu_shp <- st_read("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.shp")
cpu_df <- read.csv("E:/GreenFin/01_hra_model/_base/bz_cp_regions_3km_buffer.csv", header = TRUE, sep = ",")
```

```{r Compute 2016 km2 and % of conservation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2016/mpa_2015.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Conservation"
stressors_area$year <- "2016"
```

```{r Create a 2016 horizontal & vertical tables w results}
stressors_area -> stressors_area_2016
names(stressors_area_2016)[4] <- "cons_2016_km2" 
names(stressors_area_2016)[5] <- "cons_2016_pct" 
stressors_area_2016 <- stressors_area_2016[,c(1:5)]
write.csv(stressors_area_2016, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/conservation", paste("stressors_area_2016.csv")), row.names = F)
stressors_area -> stressors_area_2016_fig
```

```{r Compute 2020 km2 and % of conservation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2020/mpa_2020.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Conservation"
stressors_area$year <- "2020"
```

```{r Create a 2020 horizontal & vertical tables w results}
stressors_area -> stressors_area_2020
names(stressors_area_2020)[4] <- "cons_2020_km2" 
names(stressors_area_2020)[5] <- "cons_2020_pct" 
stressors_area_2020 <- stressors_area_2020[,c(1:5)]
write.csv(stressors_area_2020, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/conservation", paste("stressors_area_2020.csv")), row.names = F)
stressors_area -> stressors_area_2020_fig
```

```{r Compute 2025 km2 and % of conservation}
stressor <- st_read("E:/GreenFin/01_hra_model/2_stressor_maps/2025/mpa_2025.shp")
stressor_int_cpu <- st_intersection(stressor, cpu_shp)
stressor_int_cpu$km2 <- unclass((st_area(stressor_int_cpu))/1000000)
stressor_int_cpu$km2 <- round(stressor_int_cpu$km2, digits = 1)
stressors_area <- stressor_int_cpu %>%
  st_set_geometry(NULL) %>%
  group_by(cpu) %>%
  summarise(km2 = sum(km2))
stressors_area <- left_join(cpu_df,stressors_area, by="cpu")
stressors_area$km2[is.na(stressors_area$km2)] <- 0
stressors_area$pct <- round ((stressors_area$km2 /stressors_area$cpu_km2)*100, digits = 1)
stressors_area$stressor <- "Conservation"
stressors_area$year <- "2025"
```

```{r Create a 2025 horizontal & vertical tables w results}
stressors_area -> stressors_area_2025
names(stressors_area_2025)[4] <- "cons_2025_km2" 
names(stressors_area_2025)[5] <- "cons_2025_pct" 
stressors_area_2025 <- stressors_area_2025[,c(1:5)]
write.csv(stressors_area_2025, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/conservation", paste("stressors_area_2025.csv")), row.names = F)
stressors_area -> stressors_area_2025_fig
```

```{r Calculate conservation change from 2016}
stressors_area_all <- cbind(stressors_area_2016, stressors_area_2020, stressors_area_2025)
names(stressors_area_all)
stressors_area_all <- stressors_area_all[,c(1:5,9:10,14:15)]
stressors_area_all$dlt_2020 <- stressors_area_all$cons_2020_km2 - stressors_area_all$cons_2016_km2
stressors_area_all$dlt_2025 <- stressors_area_all$cons_2025_km2 - stressors_area_all$cons_2016_km2
stressors_area_all$dlt_pct_2020 <- round((stressors_area_all$dlt_2020/stressors_area_all$cpu_km2*100), digits = 1)
stressors_area_all$dlt_pct_2025 <- round((stressors_area_all$dlt_2025/stressors_area_all$cpu_km2*100), digits = 1)
write.csv(stressors_area_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("delta_conservation.csv")), row.names = F)
stressors_area_fig_all <- rbind(stressors_area_2016_fig, stressors_area_2020_fig, stressors_area_2025_fig)
write.csv(stressors_area_fig_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_conservation_delta.csv")), row.names = F)
```

## 9/ Make a summary table for Belize & by CPU:
```{r Combine all the stressors in absolute km2 and pct}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
stress_1 <- read.csv("fig_agric_runoff_delta.csv")
stress_2 <- read.csv("fig_aquaculture_delta.csv")
stress_3 <- read.csv("fig_development_delta.csv")
stress_4 <- read.csv("fig_dredging_delta.csv")
stress_5 <- read.csv("fig_fishing_delta.csv")
stress_6 <- read.csv("fig_oil_delta.csv")
stress_7 <- read.csv("fig_recreation_delta.csv")
stress_8 <- read.csv("fig_transportation_delta.csv")
stress_9 <- read.csv("fig_conservation_delta.csv")
stress_all <- rbind(stress_1, stress_2, stress_3, stress_4, stress_5, stress_6, stress_7, stress_8, stress_9)
write.csv(stress_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_all_stressors_delta.csv")), row.names = F)
```

```{r Combine all the stressors with the change relative 2016}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
stress_1 <- read.csv("delta_agric_runoff.csv")
stress_2 <- read.csv("delta_aquaculture.csv")
stress_3 <- read.csv("delta_development.csv")
stress_4 <- read.csv("delta_dredging.csv")
stress_5 <- read.csv("delta_fishing.csv")
stress_6 <- read.csv("delta_oil.csv")
stress_7 <- read.csv("delta_recreation.csv")
stress_8 <- read.csv("delta_transportation.csv")
stress_9 <- read.csv("delta_conservation.csv")

# extract the km2 values
stress_1_km2 <- stress_1[,c(1:2,10:11)]
stress_1_km2$stressor <- "runoff"
stress_2_km2 <- stress_2[,c(1:2,10:11)]
stress_2_km2$stressor <- "aquaculture"
stress_3_km2 <- stress_3[,c(1:2,10:11)]
stress_3_km2$stressor <- "development"
stress_4_km2 <- stress_4[,c(1:2,10:11)]
stress_4_km2$stressor <- "dredging"
stress_5_km2 <- stress_5[,c(1:2,10:11)]
stress_5_km2$stressor <- "fishing"
stress_6_km2 <- stress_6[,c(1:2,10:11)]
stress_6_km2$stressor <- "oil"
stress_7_km2 <- stress_7[,c(1:2,10:11)]
stress_7_km2$stressor <- "recreation"
stress_8_km2 <- stress_8[,c(1:2,10:11)]
stress_8_km2$stressor <- "transportation"
stress_9_km2 <- stress_9[,c(1:2,10:11)]
stress_9_km2$stressor <- "conservation"

# melt the km2 values
mstress_1_km2 <- melt(stress_1_km2, id=c("cpu","cpu_name","stressor")) 
mstress_2_km2 <- melt(stress_2_km2, id=c("cpu","cpu_name","stressor"))
mstress_3_km2 <- melt(stress_3_km2, id=c("cpu","cpu_name","stressor"))
mstress_4_km2 <- melt(stress_4_km2, id=c("cpu","cpu_name","stressor"))
mstress_5_km2 <- melt(stress_5_km2, id=c("cpu","cpu_name","stressor"))
mstress_6_km2 <- melt(stress_6_km2, id=c("cpu","cpu_name","stressor"))
mstress_7_km2 <- melt(stress_7_km2, id=c("cpu","cpu_name","stressor"))
mstress_8_km2 <- melt(stress_8_km2, id=c("cpu","cpu_name","stressor"))
mstress_9_km2 <- melt(stress_9_km2, id=c("cpu","cpu_name","stressor"))

# combine all the stressors km2 values 
stress_all <- rbind(mstress_1_km2, mstress_2_km2, mstress_3_km2, mstress_4_km2, mstress_5_km2, mstress_6_km2, mstress_7_km2, mstress_8_km2, mstress_9_km2)
write.csv(stress_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_all_stressors_delta_km2_melt.csv")), row.names = F)

# extract the percent values
stress_1_pct <- stress_1[,c(1:2,12:13)]
stress_1_pct$stressor <- "runoff"
stress_2_pct <- stress_2[,c(1:2,12:13)]
stress_2_pct$stressor <- "aquaculture"
stress_3_pct <- stress_3[,c(1:2,12:13)]
stress_3_pct$stressor <- "development"
stress_4_pct <- stress_4[,c(1:2,12:13)]
stress_4_pct$stressor <- "dredging"
stress_5_pct <- stress_5[,c(1:2,12:13)]
stress_5_pct$stressor <- "fishing"
stress_6_pct <- stress_6[,c(1:2,12:13)]
stress_6_pct$stressor <- "oil"
stress_7_pct <- stress_7[,c(1:2,12:13)]
stress_7_pct$stressor <- "recreation"
stress_8_pct <- stress_8[,c(1:2,12:13)]
stress_8_pct$stressor <- "transportation"
stress_9_pct <- stress_1[,c(1:2,12:13)]
stress_9_pct$stressor <- "conservation"

# melt the percent values
mstress_1_pct <- melt(stress_1_pct, id=c("cpu","cpu_name","stressor")) 
mstress_2_pct <- melt(stress_2_pct, id=c("cpu","cpu_name","stressor"))
mstress_3_pct <- melt(stress_3_pct, id=c("cpu","cpu_name","stressor"))
mstress_4_pct <- melt(stress_4_pct, id=c("cpu","cpu_name","stressor"))
mstress_5_pct <- melt(stress_5_pct, id=c("cpu","cpu_name","stressor"))
mstress_6_pct <- melt(stress_6_pct, id=c("cpu","cpu_name","stressor"))
mstress_7_pct <- melt(stress_7_pct, id=c("cpu","cpu_name","stressor"))
mstress_8_pct <- melt(stress_8_pct, id=c("cpu","cpu_name","stressor"))
mstress_9_pct <- melt(stress_9_pct, id=c("cpu","cpu_name","stressor"))

# combine all the stressors km2 values 
stress_all <- rbind(mstress_1_pct, mstress_2_pct, mstress_3_pct, mstress_4_pct, mstress_5_pct, mstress_6_pct, mstress_7_pct, mstress_8_pct, mstress_9_pct)
write.csv(stress_all, file.path("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/", paste("fig_all_stressors_delta_pct_melt.csv")), row.names = F)
```


## 10/ Figures in km2:

```{r Make bar chart for agriculture runoff by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_agric_runoff_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("agric_runoff"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Agriculture Runoff by Coastal Planning Unit", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_runoff.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for aquaculture by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_aquaculture_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Aquaculture"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Aquaculture by Coastal Planning Unit", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_aqua.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for development runoff by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_development_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Development"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Coastal Development by Coastal Planning Unit", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_development.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for dredging by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_dredging_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Dredging"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Dredging by Coastal Planning Unit", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_dredging.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for fishing by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_fishing_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Fishing"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Fishing by Coastal Planning Unit", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_fishing.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for oil by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_oil_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Oil"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Oil Exploration by Coastal Planning Unit", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_oil.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for recreation by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_recreation_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Fishing"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Recreation by Coastal Planning Unit", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_recreation.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```


```{r Make bar chart for transportation by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_transportation_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Transportation"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Transportation by Coastal Planning Unit", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_transportation.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r figure for Belize showing the change in stressors by year}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_all_stressors_delta.csv")
# select belize rows only
results <- results[results$cpu == '10',]
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Runoff","Aquaculture","Development", "Dredging","Fishing","Oil","Recreation","Transportation"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_name <- factor(results$cpu_name,  # Change ordering manually
                              levels = c("Belize"))
## set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=km2, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in stressors", x = "", y = bquote("Area "(km^2)), fill = "Years:") +
  facet_wrap("stressor", scales = "free_y", nrow = 2) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_bz.pdf")),
    width = 7, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

## 10/ Figures in percent:

```{r Make bar chart for agriculture runoff by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_agric_runoff_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("agric_runoff"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Agriculture Runoff by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_runoff_pct.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for aquaculture by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_aquaculture_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Aquaculture"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Aquaculture by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_aqua.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for development by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_development_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Development"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Coastal Development by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_development.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for dredging by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_dredging_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Dredging"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Dredging by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_dredging.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for fishing by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_fishing_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Fishing"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Fishing by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_fishing.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for oil by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_oil_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Oil"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Oil Exploration by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_oil.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for recreation by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_recreation_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Fishing"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Recreation by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_recreation.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```


```{r Make bar chart for transportation by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_transportation_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Transportation"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Transportation by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_transportation.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r Make bar chart for Conservation by CPU}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_conservation_delta.csv")
# select cpu rows only
target <- c('1','2','3','4','5','6','7','8','9')
results <- results[results$cpu %in% target,] 
results$cpu_nb_name <- paste(results$cpu,results$cpu_name,sep= "-")
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Conservation"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_nb_name <- factor(results$cpu_nb_name, levels = c("1-Northern Region", "2-Ambergris Caye","3-Caye Caulker","4-Central Region","5-Turneffe Atoll","6-Lighthouse Reef Atoll","7-South Northern Region","8-South Central Region","9-Southern Region"))
# set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in Conservation by Coastal Planning Unit", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("cpu_nb_name", nrow = 3) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_cpu_conservation.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```

```{r figure for Belize showing the change in stressors by year}
setwd("E:/GreenFin/01_hra_model/2_stressor_maps/cpu_analysis/")
# import dataframe
results <- read.csv("fig_all_stressors_delta.csv")
# select belize rows only
results <- results[results$cpu == '10',]
# set the order for the stressors
results$stressor <- factor(results$stressor,  # Change ordering manually
                          levels = c("Runoff","Aquaculture","Development", "Dredging","Fishing","Oil","Recreation","Transportation"))
# set the order for the years
results$year <- factor(results$year,  # Change ordering manually
                          levels = c("2016", "2020", "2025"))
# set the order of planning units (north to south)
results$cpu_name <- factor(results$cpu_name,  # Change ordering manually
                              levels = c("Belize"))
## set custom colors
 year_cols <- c("darkgrey", "grey", "black")
 names(year_cols) <- c("2016", "2020", "2025")
# build the bar chart
ggbars <- ggplot(results) +
  geom_bar(aes(x=year, y=pct, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Change in stressors", x = "", y = "Area (%)", fill = "Years:") +
  facet_wrap("stressor", scales = "free_y", nrow = 2) +
  theme_bw() +
  theme(axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
# export and displays as values
pdf(file.path("E:/GreenFin/01_hra_model/2_stressor_maps", paste("_barplot_change_stressors_area_bz_pct.pdf")),
    width = 7, height = 5)
plot_grid(ggbars + scale_y_continuous(labels = scales::comma))
dev.off()
```
