---
title: "Post process the Recreation models outputs using the habitat maps from 2016"
author: "Jade Delevaux"
created: August 2020
output:
  pdf_document: default
  html_document:
    df_print: paged
---

To run this script, install the packages below

```{r Install packages}
library(sf)
library(foreign)
library(raster)
library(rgdal)
library(dplyr)
library(exactextractr) # quick zonal stat
library(ggplot2)
library(gridExtra)
library(cowplot)
library(rgeos)
library(sp)
library(ggpubr)
library(tigris)
library(maptools)
library(reshape)
```

REC outputs a shapefile map for each scenario (2016 = baseline, 2020 = current, and 2025 = informed management), which shows the visitation patterns in photo-users days across the area of interest. We need to combine those shapefiles to (1) calculate the change in visitation compared to 2016 and (2) summarize the change at the Belize scale and by coastal planning units.

Note: The working directory (WD) needs to reflect your local machine. Use the function "Find and replace" in R studio to replace the root of the working directory by your local path (e.g., "E:/GreenFin") to apply this script. 

First run the InVEST Recreation model for the baseline (2016) with the two scenarios (2020 and 2025).

# 1/ Combine the results from the three InVEST runs
Import the results into R workspace
```{r Import the REC model results}
rec_output_shp_2016_all <- st_read("E:/Greenfin/03_recreation/rec_outputs/2016_habitats/pud_results_2016_2020.shp")
rec_output_shp_2020_all <- st_read("E:/Greenfin/03_recreation/rec_outputs/2016_habitats/scenario_results_2016_2020.shp")
rec_output_shp_2025_all <- st_read("E:/Greenfin/03_recreation/rec_outputs/2016_habitats/scenario_results_2016_2025.shp")
```

Merge the three files and only keep the visitation data from each file:
```{r merge all the results}
names(rec_output_shp_2016_all)
rec_output_shp_2016 <- rec_output_shp_2016_all[,c(1:7,20)]
names(rec_output_shp_2016)[7] <- 'PUD2016'
names(rec_output_shp_2020_all)
rec_output_shp_2020 <- rec_output_shp_2020_all[,c(14)]
names(rec_output_shp_2020)[1] <- 'PUD2020'
names(rec_output_shp_2025_all)
rec_output_shp_2025 <- rec_output_shp_2025_all[,c(14)]
names(rec_output_shp_2025)[1] <- 'PUD2025'
rec_output <- cbind(rec_output_shp_2016, rec_output_shp_2020, rec_output_shp_2025)
rec_output <- rec_output[,-c(11:12)]
```

# 2/ Spread the Total Person Days by time step
Calculate the total number of person days (PDT) for 2016, 2020 and 2025, based on the number of visitors from the BTB (refer to CZMAI plan and BTB dashboard). Then use the Photo-User Days (PUD) to spread spatially the Total-Person Days (TPD):
```{r calculate total person days}
total_pud_2016 <- sum(rec_output$PUD2016)
total_visitors_2016 <- 2229627
rec_output$TPD2016 <- rec_output$PUD2016*total_visitors_2016/total_pud_2016
total_pud_2020 <- sum(rec_output$PUD2020)
total_visitors_2020 <- 1263885
rec_output$TPD2020 <- rec_output$PUD2020*total_visitors_2020/total_pud_2020
total_pud_2025 <- sum(rec_output$PUD2025)
total_visitors_2025 <- 5471264
rec_output$TPD2025 <- rec_output$PUD2025*total_visitors_2025/total_pud_2025
```

Calculate the change in visitation relative to 2016:
```{r calculate change in person days}
rec_output$DLT2020 <- rec_output$TPD2020-rec_output$TPD2016
rec_output$DLT2025 <- rec_output$TPD2025-rec_output$TPD2016
```

# 3/ Calculate the percent of overnight and cruise visitors per time step
We need to spatially spread the Total-Person Days values based on the PUD values. To do so, we first need to determine the percent of overnight and cruise visitors each time step to dostribute each based on the PUD for each time step. 

Calculate the percent and number of overnight and cruise visitors for 2016. Refer to the equation 1 from the CZMAI plan to understand how the values were selected (see section B3):
```{r Calculate the percent and number of visitor type in 2016}
coastal_visitation_factor <- 0.74
overnight_visitors_2016 <- 277135
overnight_length_days_2016 <- 8.56
cruise_visitors_2016 <- 640734
cruise_length_days_2016 <- 1
total_visitors_2016 <-2229627
pct_overnight_visitors_2016 <- (coastal_visitation_factor * overnight_visitors_2016 * overnight_length_days_2016)/total_visitors_2016
pct_cruise_visitors_2016 <- (coastal_visitation_factor * cruise_visitors_2016 * cruise_length_days_2016)/total_visitors_2016
```

Calculate the percent and number of overnight and cruise visitors for 2020 (Refer to guidance note for more details on how the the values were selected)
```{r Calculate the percent and number of visitor type in 2020}
coastal_visitation_factor <- 0.74
overnight_visitors_2020 <- 144124
overnight_length_days_2020 <- 9.47
cruise_visitors_2020 <- 343099
cruise_length_days_2020 <- 1
total_visitors_2020 <-1707953
pct_overnight_visitors_2020 <- (coastal_visitation_factor * overnight_visitors_2020 * overnight_length_days_2020)/total_visitors_2020
pct_cruise_visitors_2020 <- (coastal_visitation_factor * cruise_visitors_2020 * cruise_length_days_2020)/total_visitors_2020
```

Calculate the percent and number of overnight and cruise visitors for 2025. Refer to the equation 1 from the CZMAI plan to understand how the values were selected (see section B3):
```{r Calculate the percent and number of visitor type in 2025}
coastal_visitation_factor <- 0.74
overnight_visitors_2025 <- 556000
overnight_length_days_2025 <- 10.6
cruise_visitors_2025 <- 1500000
cruise_length_days_2025 <- 1
total_visitors_2025 <-5471264
pct_overnight_visitors_2025 <- (coastal_visitation_factor * overnight_visitors_2025 * overnight_length_days_2025)/total_visitors_2025
pct_cruise_visitors_2025 <- (coastal_visitation_factor * cruise_visitors_2025 * cruise_length_days_2025)/total_visitors_2025
```

# 4/ Calculate the number of overnight and cruise visitors
Calculate the number of overnight and cruise visitors for 2016, 2020 and 2025 to derive the revenue from tourism
```{r Calculate the number of visitor day type for each scenario}
rec_output$NIT2016 <- rec_output$TPD2016*pct_overnight_visitors_2016
rec_output$SHP2016 <- rec_output$TPD2016*pct_cruise_visitors_2016
rec_output$NIT2020 <- rec_output$TPD2020*pct_overnight_visitors_2020
rec_output$SHP2020 <- rec_output$TPD2020*pct_cruise_visitors_2020
rec_output$NIT2025 <- rec_output$TPD2025*pct_overnight_visitors_2025
rec_output$SHP2025 <- rec_output$TPD2025*pct_cruise_visitors_2025
```

# 5/ Calculate the annual expenditure per type of visitors
calculate the annual expenditure per visitor type and for the total number of person-days for 2016,2020, and 2025:
```{r Calculate annual expenditure for each scenario}
overnight_visitor_daily_expenditure_2016 <- 133
cruise_visitor_daily_expenditure_2016 <- 57
overnight_visitor_daily_expenditure_2020 <- 153
cruise_visitor_daily_expenditure_2020 <- 71
overnight_visitor_daily_expenditure_2025 <- 195
cruise_visitor_daily_expenditure_2025 <- 83
rec_output$USD2016 <- rec_output$NIT2016*overnight_visitor_daily_expenditure_2016 + rec_output$SHP2016*cruise_visitor_daily_expenditure_2016
rec_output$USD2020 <- rec_output$NIT2020*overnight_visitor_daily_expenditure_2020 + rec_output$SHP2020*cruise_visitor_daily_expenditure_2020
rec_output$USD2025 <- rec_output$NIT2025*overnight_visitor_daily_expenditure_2025 + rec_output$SHP2025*cruise_visitor_daily_expenditure_2025
```

# 6/ Export results in shapefile and csv file
Export the results into a shapefile and csv table
```{r Export shp and csv results}
rec_output_sp <- as(rec_output, "Spatial")
class(rec_output_sp)
writeOGR(obj=rec_output_sp, dsn="E:/Greenfin/03_recreation/rec_outputs/2016_habitats", layer="rec_output", driver="ESRI Shapefile", overwrite_layer =  T)
rec_output <- as.data.frame(rec_output_sp)
names(rec_output)
write.csv(rec_output, file.path("E:/Greenfin/03_recreation/rec_outputs/2016_habitats", paste("rec_summary.csv")), row.names = F)
```

Summarize results by coastal planning units & add the CPU names:
```{r Summarize results by coastal planning units}
rec_output$cpu <- as.factor(rec_output$cpu)
rec_output$cpu_name <- as.factor(rec_output$cpu_name)
rec_output$cpuwname <- paste(rec_output$cpu,rec_output$cpu_name,sep= "-")
rec_output$cpuwname <- as.factor(rec_output$cpuwname)
rec_output_by_cpu <- aggregate(rec_output[,-c(1:6,24)],rec_output[c("cpu","cpu_name","cpuwname")],sum)
bz_total<-data.frame("10","Belize","10-Belize", t(colSums(rec_output_by_cpu[,-c(1:3)])))
names(bz_total)[1] <- "cpu"
names(bz_total)[2] <- "cpu_name"
names(bz_total)[3] <- "cpuwname"
write.csv(bz_total, file.path("E:/Greenfin/03_recreation/rec_outputs/2016_habitats", paste("rec_summary_by_bz.csv")), row.names = F)
write.csv(rec_output_by_cpu, file.path("E:/Greenfin/03_recreation/rec_outputs/2016_habitats", paste("rec_summary_by_cpu.csv")), row.names = F)
```

# 7/ Create table for figures
Create a dataframe to make a bar chart by coastal planning unit to display change in Total Person Days:
```{r Create dataframe for Total Person Days by coastal planning units}
names(rec_output_by_cpu)
rec_output_by_cpu_tpd_2016 <- rec_output_by_cpu[,c(1:3,7)]
rec_output_by_cpu_tpd_2016$Year <- "2016" 
names(rec_output_by_cpu_tpd_2016)
rec_output_by_cpu_tpd_2016_flip <- melt(rec_output_by_cpu_tpd_2016, id=c("cpu","cpu_name","cpuwname","Year")) 
str(rec_output_by_cpu_tpd_2016_flip) 
names(rec_output_by_cpu_tpd_2016_flip)[6] <- "TPD" 
rec_output_by_cpu_tpd_2020 <- rec_output_by_cpu[,c(1:3,8)]
rec_output_by_cpu_tpd_2020$Year <- "2020" 
names(rec_output_by_cpu_tpd_2020)
rec_output_by_cpu_tpd_2020_flip <- melt(rec_output_by_cpu_tpd_2020, id=c("cpu","cpu_name","cpuwname","Year")) 
str(rec_output_by_cpu_tpd_2020_flip) 
names(rec_output_by_cpu_tpd_2020_flip)[6] <- "TPD" 
rec_output_by_cpu_tpd_2025 <- rec_output_by_cpu[,c(1:3,9)]
rec_output_by_cpu_tpd_2025$Year <- "2025" 
names(rec_output_by_cpu_tpd_2025)
rec_output_by_cpu_tpd_2025_flip <- melt(rec_output_by_cpu_tpd_2025, id=c("cpu","cpu_name","cpuwname","Year")) 
str(rec_output_by_cpu_tpd_2025_flip) 
names(rec_output_by_cpu_tpd_2025_flip)[6] <- "TPD" 
rec_output_by_cpu_tpd <- rbind(rec_output_by_cpu_tpd_2016_flip, rec_output_by_cpu_tpd_2020_flip, rec_output_by_cpu_tpd_2025_flip) 
rec_output_by_cpu_tpd <- rec_output_by_cpu_tpd[,c(1:4,6)]
names(rec_output_by_cpu_tpd)
rec_output_by_cpu_tpd$REC.model <- "Total Person Days"
write.csv(rec_output_by_cpu_tpd, file.path("E:/Greenfin/03_recreation/rec_outputs/2016_habitats", paste("rec_summary_by_cpu_tpd.csv")), row.names = F)
```

Create a dataframe to make a bar chart by coastal planning unit to display change in Expenditure:
```{r Create dataframe for Annual Expenditure by coastal planning units}
names(rec_output_by_cpu)
rec_output_by_cpu_usd_2016 <- rec_output_by_cpu[,c(1:3,18)]
rec_output_by_cpu_usd_2016$Year <- "2016" 
names(rec_output_by_cpu_usd_2016)
rec_output_by_cpu_usd_2016_flip <- melt(rec_output_by_cpu_usd_2016, id=c("cpu","cpu_name","cpuwname","Year")) 
str(rec_output_by_cpu_usd_2016_flip) 
names(rec_output_by_cpu_usd_2016_flip)[6] <- "USD" 
rec_output_by_cpu_usd_2020 <- rec_output_by_cpu[,c(1:3,19)]
rec_output_by_cpu_usd_2020$Year <- "2020" 
names(rec_output_by_cpu_usd_2020)
rec_output_by_cpu_usd_2020_flip <- melt(rec_output_by_cpu_usd_2020, id=c("cpu","cpu_name","cpuwname","Year")) 
str(rec_output_by_cpu_usd_2020_flip) 
names(rec_output_by_cpu_usd_2020_flip)[6] <- "USD" 
rec_output_by_cpu_usd_2025 <- rec_output_by_cpu[,c(1:3,20)]
rec_output_by_cpu_usd_2025$Year <- "2025" 
names(rec_output_by_cpu_usd_2025)
rec_output_by_cpu_usd_2025_flip <- melt(rec_output_by_cpu_usd_2025, id=c("cpu","cpu_name","cpuwname","Year")) 
str(rec_output_by_cpu_usd_2025_flip) 
names(rec_output_by_cpu_usd_2025_flip)[6] <- "USD" 
rec_output_by_cpu_usd <- rbind(rec_output_by_cpu_usd_2016_flip, rec_output_by_cpu_usd_2020_flip, rec_output_by_cpu_usd_2025_flip) 
rec_output_by_cpu_usd <- rec_output_by_cpu_usd[,c(1:4,6)]
names(rec_output_by_cpu_usd)
rec_output_by_cpu_usd$REC.model <- "Tourism Revenue"
write.csv(rec_output_by_cpu_usd, file.path("E:/Greenfin/03_recreation/rec_outputs/2016_habitats", paste("rec_summary_by_cpu_usd.csv")), row.names = F)
```

# 8/ Summarize the results into bar charts:
Create bar chart on Total Person Days by CPU
```{r Build bar chart on Total Person Days by CPU}
rec_outputs <- read.csv("E:/Greenfin/03_recreation/rec_outputs/2016_habitats/rec_summary_by_cpu_tpd.csv")
rec_outputs$REC.model <- factor(rec_outputs$REC.model,
                                   levels = c("Total Person Days"))
rec_outputs$Year <- factor(rec_outputs$Year,  
                          levels = c("2025", "2020", "2016"))
rec_outputs$cpuwname <- factor(rec_outputs$cpuwname,  # Change ordering manually
                          levels = c("9-Southern Region","8-South Central Region","7-South Northern Region","6-Lighthouse Reef Atoll","5-Turneffe Atoll","4-Central Region","3-Caye Caulker","2-Ambergris Caye","1-Northern Region"))
rec_outputs$TPD <-as.numeric(rec_outputs$TPD)
year_cols <- c("deepskyblue", "darkorchid", "deeppink")
names(year_cols) <- c("2016", "2020", "2025")
ggbars <- ggplot(rec_outputs) +
  geom_bar(aes(x=cpuwname, y=TPD, fill=Year), position="dodge", stat="identity")+
  scale_fill_manual(values=year_cols) +
  labs(title = "Total-Person Days", x = "Coastal Planning Units", y = "Total-Person Days") +
  facet_wrap("REC.model") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 12, face="bold"), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text.x = element_text(angle = 45, hjust = 0.7, vjust = 0.8),
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
pdf(file.path("E:/Greenfin/03_recreation/rec_outputs/2016_habitats", paste("_barplot_cpu_rec_outputs_tpd.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
dev.off()
```

Create bar chart on tourism annual expenditure by CPU
```{r Build bar chart on Annual expenditure by CPU}
rec_outputs <- read.csv("E:/Greenfin/03_recreation/rec_outputs/2016_habitats/rec_summary_by_cpu_usd.csv")
rec_outputs$REC.model <- factor(rec_outputs$REC.model,
                                   levels = c("Tourism Revenue"))
rec_outputs$USDx10000 <- rec_outputs$USD/10000
names(rec_outputs)
rec_outputs$Year <- factor(rec_outputs$Year,
                           levels = c("2025", "2020", "2016"))
rec_outputs$cpuwname <- factor(rec_outputs$cpuwname,  # Change ordering manually
                          levels = c("9-Southern Region","8-South Central Region","7-South Northern Region","6-Lighthouse Reef Atoll","5-Turneffe Atoll","4-Central Region","3-Caye Caulker","2-Ambergris Caye","1-Northern Region"))
year_cols <- c("deepskyblue", "darkorchid", "deeppink")
names(year_cols) <- c("2016", "2020", "2025")
ggbars <- ggplot(rec_outputs) +
  geom_bar(aes(x=cpuwname, y=USDx10000, fill=Year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Tourism Annual Expenditure", x = "Coastal Planning Units", y = "Annual Expenditure (USD x 10,000)") +
  facet_wrap("REC.model") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 12, face="bold"), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text.x = element_text(angle = 45, hjust = 0.7, vjust = 0.8),
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
pdf(file.path("E:/Greenfin/03_recreation/rec_outputs/2016_habitats", paste("_barplot_cpu_rec_outputs_usd.pdf")),
    width = 8, height = 5)
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
dev.off()
```

Clear the working environment 
```{r Clear workspace}
rm(list = ls(all.names=TRUE))
```
