---
title: "Post process the Coastal Vulnerability model outputs using the habitat maps from 2016"
author: "Jade Delevaux"
created: September 2022
output:
  html_document:
    df_print: paged
---

To run this script, install the packages below

```{r Install packages}
library(sf)
library(foreign)
library(raster)
library(rgdal)
library(dplyr)
library(exactextractr) # quick zonal stat
library(ggplot2)
library(gridExtra)
library(cowplot)
library(rgeos)
library(sp)
library(ggpubr)
library(tigris)
library(maptools)
library(buffeRs)
library(matrixStats)
```

# A/ Quantify the habitat importance at protecting the coastline for all the scenarios (2016, 2020, 2025) relative to the 2016 No Habitat EI:

We are interested in assessing the role of habitat in providing coastal protection. To do so, we need to compare the coastal exposure index from our three timeline scenarios (2016, 2020, and 2025) in relation to the exposure index without habitat from 2016. In total, we have 4 scenarios.  

We will reclassify the CV results using the Exposure Index from our 4 scenarios in terms of low, low-medium, medium-high, and high risk. We extract the EI values for each year and stack the database:

```{r Extract and stack 2016 no habitat results}
cv_2016 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2016/cv_ei_w_hra.shp")
names(cv_2016)
cv_df <- as.data.frame(cv_2016)
cv_ei <- as.data.frame(cv_df[,c(25)])
names(cv_ei)[1] <- "2016_noh"
cv_ei$year <- "2016"
scenario_stack_1 <- reshape2::melt(cv_ei, id=c("year"))
names(scenario_stack_1)[3] <- "ei"
scenario_stack_1$habitat <- "non"
scenario_stack_1 <- as.data.frame(scenario_stack_1[,-c(2)])
```

```{r Extract and stack 2016 with HRA habitat results}
cv_2016 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2016/cv_ei_w_hra.shp")
names(cv_2016)
cv_df <- as.data.frame(cv_2016)
cv_ei <- as.data.frame(cv_df[,c(24)])
names(cv_ei)[1] <- "2016_hra"
cv_ei$year <- "2016"
scenario_stack_2 <- reshape2::melt(cv_ei, id=c("year"))
names(scenario_stack_2)[3] <- "ei"
scenario_stack_2$habitat <- "hra"
scenario_stack_2 <- as.data.frame(scenario_stack_2[,-c(2)])
```

```{r Extract and stack 2020 HRA habitat results}
cv_2020 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2020/cv_ei_w_hra.shp")
names(cv_2020)
cv_df <- as.data.frame(cv_2020)
cv_ei <- as.data.frame(cv_df[,c(24)])
names(cv_ei)[1] <- "2020_hra"
cv_ei$year <- "2020"
scenario_stack_3 <- reshape2::melt(cv_ei, id=c("year"))
names(scenario_stack_3)[3] <- "ei"
scenario_stack_3$habitat <- "hra"
scenario_stack_3 <- as.data.frame(scenario_stack_3[,-c(2)])
```

```{r Extract and stack 2025 HRA habitat results}
cv_2025 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2025/cv_ei_w_hra.shp")
names(cv_2025)
cv_df <- as.data.frame(cv_2025)
cv_ei <- as.data.frame(cv_df[,c(24)])
names(cv_ei)[1] <- "2025_hra"
cv_ei$year <- "2025"
scenario_stack_4 <- reshape2::melt(cv_ei, id=c("year"))
names(scenario_stack_4)[3] <- "ei"
scenario_stack_4$habitat <- "hra"
scenario_stack_4 <- as.data.frame(scenario_stack_4[,-c(2)])
```

We combine the databases from the 3 timelines and the no habitat 2016 scenario to determine the breaks for the quantiles breaks to use in the reclassification::
```{r Identify the 4 quantiles breaks}
cv_all_scenarios <- rbind (scenario_stack_1, 
                           scenario_stack_2, 
                           scenario_stack_3, 
                           scenario_stack_4)
ei = cv_all_scenarios$ei
quantile(ei, prob=c(.25,.5,.75, 1)) 
```

Then we reclassify the results as low (<25%) (coded as 1), medium-low (25-50%) (coded as 2), medium-high (50-75%)  (coded as 3), high (75-100%) (coded as 4):
```{r Reclassify 2016 no habitat results}
cv_2016$eic_noh[cv_2016$ei_noh <= quantile(ei, prob=c(.25))] <- 1
cv_2016$eic_noh[cv_2016$ei_noh > quantile(ei, prob=c(.25)) & cv_2016$ei_noh <= quantile(ei, prob=c(.5))] <- 2
cv_2016$eic_noh[cv_2016$ei_noh > quantile(ei, prob=c(.5)) & cv_2016$ei_noh <= quantile(ei, prob=c(.75))] <- 3
cv_2016$eic_noh[cv_2016$ei_noh > quantile(ei, prob=c(.75)) & cv_2016$ei_noh <= '5'] <- 4
```

```{r Reclassify 2016 hra habitat results}
cv_2016$eic_hra[cv_2016$ei_hra <= quantile(ei, prob=c(.25))] <- 1
cv_2016$eic_hra[cv_2016$ei_hra > quantile(ei, prob=c(.25)) & cv_2016$ei_hra <= quantile(ei, prob=c(.5))] <- 2
cv_2016$eic_hra[cv_2016$ei_hra > quantile(ei, prob=c(.5)) & cv_2016$ei_hra <= quantile(ei, prob=c(.75))] <- 3
cv_2016$eic_hra[cv_2016$ei_hra > quantile(ei, prob=c(.75)) & cv_2016$ei_hra <= '5'] <- 4
```

```{r Reclassify 2020 hra habitat results}
cv_2020$eic_hra[cv_2020$ei_hra <= quantile(ei, prob=c(.25))] <- 1
cv_2020$eic_hra[cv_2020$ei_hra > quantile(ei, prob=c(.25)) & cv_2020$ei_hra <= quantile(ei, prob=c(.5))] <- 2
cv_2020$eic_hra[cv_2020$ei_hra > quantile(ei, prob=c(.5)) & cv_2020$ei_hra <= quantile(ei, prob=c(.75))] <- 3
cv_2020$eic_hra[cv_2020$ei_hra > quantile(ei, prob=c(.75)) & cv_2020$ei_hra <= '5'] <- 4
```

```{r Reclassify 2025 hra habitat results}
cv_2025$eic_hra[cv_2025$ei_hra <= quantile(ei, prob=c(.25))] <- 1
cv_2025$eic_hra[cv_2025$ei_hra > quantile(ei, prob=c(.25)) & cv_2025$ei_hra <= quantile(ei, prob=c(.5))] <- 2
cv_2025$eic_hra[cv_2025$ei_hra > quantile(ei, prob=c(.5)) & cv_2025$ei_hra <= quantile(ei, prob=c(.75))] <- 3
cv_2025$eic_hra[cv_2025$ei_hra > quantile(ei, prob=c(.75)) & cv_2025$ei_hra <= '5'] <- 4
```

Calculate the difference between the scenarios with the HRA habitat and the 2016 no habitat scenario to evaluate whether the shoreline point changes quantile, which indicates  that habitat provides some shoreline protection: 
```{r Calculate the change for all the risk class due to the habitat}
cv_2016$risk_dlt <- cv_2016$eic_noh - cv_2016$eic_hra
cv_2020$risk_dlt <- cv_2016$eic_noh - cv_2020$eic_hra
cv_2025$risk_dlt <- cv_2016$eic_noh - cv_2025$eic_hra
```

Then we export the results as shapefile and csv:
```{r Export 2016 results as shp and csv}
cv_2016_sp <- as(cv_2016, "Spatial")
class(cv_2016_sp)
writeOGR(obj=cv_2016_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2016/", layer="cv_2016_ei_reclass", driver="ESRI Shapefile", overwrite_layer =  T)
cv_2016_df <- as.data.frame(cv_2016_sp)
names(cv_2016_df)
cv_2016_df <- cv_2016_df[,-c(30:31)]# delete coord
names(cv_2016_df)
write.csv(cv_2016_df, paste0("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2016/", "cv_2016_ei_reclass.csv"), row.names = F)
```

```{r Export 2020 results as shp and csv}
cv_2020_sp <- as(cv_2020, "Spatial")
class(cv_2020_sp)
writeOGR(obj=cv_2020_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2020/", layer="cv_2020_ei_reclass", driver="ESRI Shapefile", overwrite_layer =  T)
cv_2020_df <- as.data.frame(cv_2020_sp)
names(cv_2020_df)
cv_2020_df <- cv_2020_df[,-c(29:30)]# delete coord
names(cv_2020_df)
write.csv(cv_2020_df, paste0("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2020/", "cv_2020_ei_reclass.csv"), row.names = F)
```

```{r Export 2025 results as shp and csv}
cv_2025_sp <- as(cv_2025, "Spatial")
class(cv_2025_sp)
writeOGR(obj=cv_2025_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2025/", layer="cv_2025_ei_reclass", driver="ESRI Shapefile", overwrite_layer =  T)
cv_2025_df <- as.data.frame(cv_2025_sp)
names(cv_2020_df)
cv_2025_df <- cv_2025_df[,-c(29:30)]# delete coord
names(cv_2025_df)
write.csv(cv_2025_df, paste0("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2025/", "cv_2025_ei_reclass.csv"), row.names = F)
```

Last, clear working environment
```{r Clear the workspace}
rm(list = ls(all.names=TRUE))
```

# B/ Summarize the # of km and people benefit from coastal habitat protection for all the scenarios (2016, 2020, 2025) by coastal planning units:

We need to summarize our results in two ways:
1/ Quantify how many km are less exposed to any level of risk thanks to coastal and marine habitats
2/ Quantify how many km become not exposed to high risk thanks to the presence of coastal and marine habitats

## B.1/ Change in risk exposure class due to habitat 
We need to count the number of shoreline points within each coastal planning unit to compute the number of shoreline km that becomes less exposed to coastal hazard due to the presence of habitats:

```{r Count the number of people changing EI class in 2016}
people_2016 <- raster("E:/GreenFin/02_cv_model/cv_inputs/bz_ppp_2016_2km_mean.tif")
NAvalue(people_2016) <- -9999
cv_2016 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2016/cv_2016_ei_reclass.shp")
names(cv_2016)
cv_2016$cpu<- as.factor(cv_2016$cpu)
cv_2016$risk_dlt <- as.factor(cv_2016$risk_dlt)
cv_2016 <- cv_2016[,c(1,12,27:29)]
target <- c('1','2','3')
cv_2016 <- cv_2016[cv_2016$risk_dlt %in% target,] 
cv_2016$ppl_raw <- raster::extract(people_2016, cv_2016, method='simple')
cv_2016$ppl <- cv_2016$ppl_raw*25
cv_2016_risk_delta_sp <- as(cv_2016, "Spatial")
class(cv_2016_risk_delta_sp)
writeOGR(obj=cv_2016_risk_delta_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2016", layer="cv_2016_ei_reclass_delta_w_people", driver="ESRI Shapefile", overwrite_layer =  T)
```

Do the same for 2020
```{r Count the number of people changing EI class in 2020}
people_2020 <- raster("E:/GreenFin/02_cv_model/cv_inputs/bz_ppp_2020_2km_mean.tif")
NAvalue(people_2020) <- -9999
cv_2020 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2020/cv_2020_ei_reclass.shp")
names(cv_2020)
cv_2020$cpu<- as.factor(cv_2020$cpu)
cv_2020$risk_dlt <- as.factor(cv_2020$risk_dlt)
cv_2020 <- cv_2020[,c(1,12,27:28)]
target <- c('1','2','3')
cv_2020 <- cv_2020[cv_2020$risk_dlt %in% target,] 
cv_2020$ppl_raw <- raster::extract(people_2020, cv_2020, method='simple')
cv_2020$ppl <- cv_2020$ppl_raw*25
cv_2020_risk_delta_sp <- as(cv_2020, "Spatial")
class(cv_2020_risk_delta_sp)
writeOGR(obj=cv_2020_risk_delta_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2020", layer="cv_2020_ei_reclass_delta_w_people", driver="ESRI Shapefile", overwrite_layer =  T)
```

And 2025
```{r Count the number of people changing EI class in 2025}
people_2020 <- raster("E:/GreenFin/02_cv_model/cv_inputs/bz_ppp_2020_2km_mean.tif")
NAvalue(people_2020) <- -9999
cv_2025 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2025/cv_2025_ei_reclass.shp")
names(cv_2025)
cv_2025$cpu<- as.factor(cv_2025$cpu)
cv_2025$risk_dlt <- as.factor(cv_2025$risk_dlt)
cv_2025 <- cv_2025[,c(1,12,27:28)]
target <- c('1','2','3')
cv_2025 <- cv_2025[cv_2025$risk_dlt %in% target,] 
cv_2025$ppl_raw <- raster::extract(people_2020, cv_2025, method='simple')
cv_2025$ppl <- cv_2025$ppl_raw*25
cv_2025_risk_delta_sp <- as(cv_2025, "Spatial")
class(cv_2025_risk_delta_sp)
writeOGR(obj=cv_2025_risk_delta_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2025", layer="cv_2025_ei_reclass_delta_w_people", driver="ESRI Shapefile", overwrite_layer =  T)
```

Combine the values from people and km of shoreline at lesser risk from the 3 timelines into 1 to create summary tables for figures and metrics reporting
```{r Compute the number of km and people protected by habitats per CPU for each scenarios}
# 2016
cv_2016_risk_delta <- as.data.frame(cv_2016_risk_delta_sp)
cv_2016_risk_delta_km <- aggregate(shore_id ~ cpu, data = cv_2016_risk_delta, FUN = length)
cv_2016_risk_delta_km$km <- cv_2016_risk_delta_km$shore_id/4
cv_2016_risk_delta <- cv_2016_risk_delta[,c(2,7)] 
cv_2016_risk_delta_ppl <- aggregate(.~ cpu, data = cv_2016_risk_delta, FUN = sum)
cv_2016_risk_delta_ppl$ppl <- as.integer(cv_2016_risk_delta_ppl$ppl, digit=0)
cv_2016_risk_delta_by_cpu <- cbind(cv_2016_risk_delta_km,cv_2016_risk_delta_ppl)
cv_2016_risk_delta_by_cpu <- cv_2016_risk_delta_by_cpu[,-c(4)]
cv_2016_risk_delta_by_cpu$year <- "2016"
# 2020
cv_2020_risk_delta <- as.data.frame(cv_2020_risk_delta_sp)
cv_2020_risk_delta_km <- aggregate(shore_id ~ cpu, data = cv_2020_risk_delta, FUN = length)
cv_2020_risk_delta_km$km <- cv_2020_risk_delta_km$shore_id/4
cv_2020_risk_delta <- cv_2020_risk_delta[,c(2,6)] 
cv_2020_risk_delta_ppl <- aggregate(.~ cpu, data = cv_2020_risk_delta, FUN = sum)
cv_2020_risk_delta_ppl$ppl <- as.integer(cv_2020_risk_delta_ppl$ppl, digit=0)
cv_2020_risk_delta_by_cpu <- cbind(cv_2020_risk_delta_km,cv_2020_risk_delta_ppl)
cv_2020_risk_delta_by_cpu <- cv_2020_risk_delta_by_cpu[,-c(4)]
cv_2020_risk_delta_by_cpu$year <- "2020"
# 2025
cv_2025_risk_delta <- as.data.frame(cv_2025_risk_delta_sp)
cv_2025_risk_delta_km <- aggregate(shore_id ~ cpu, data = cv_2025_risk_delta, FUN = length)
cv_2025_risk_delta_km$km <- cv_2025_risk_delta_km$shore_id/4
cv_2025_risk_delta <- cv_2025_risk_delta[,c(2,6)] 
cv_2025_risk_delta_ppl <- aggregate(.~ cpu, data = cv_2025_risk_delta, FUN = sum)
cv_2025_risk_delta_ppl$ppl <- as.integer(cv_2025_risk_delta_ppl$ppl, digit=0)
cv_2025_risk_delta_by_cpu <- cbind(cv_2025_risk_delta_km,cv_2025_risk_delta_ppl)
cv_2025_risk_delta_by_cpu <- cv_2025_risk_delta_by_cpu[,-c(4)]
cv_2025_risk_delta_by_cpu$year <- "2025"
# combine
cv_risk_delta_by_cpu <- rbind(cv_2016_risk_delta_by_cpu, cv_2020_risk_delta_by_cpu, cv_2025_risk_delta_by_cpu)
write.csv(cv_risk_delta_by_cpu, paste0("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/", "cv_ei_delta_km_ppl_by_cpu.csv"), row.names = F)
```

## B.2/ Change in high risk exposure due to habitat 
We need to count the number of shoreline points within each coastal planning unit to compute the number of shoreline km that becomes not at high risk due to the presence of habitats:

We are also interested in determining which section of the shoreline becomes less at High risk due to habitat. To do so, we need to compare the EI to the scenario No habitat High EI from 2016: 
```{r Count the number of people changing EI class high in 2016}
people_2016 <- raster("E:/GreenFin/02_cv_model/cv_inputs/bz_ppp_2016_2km_mean.tif")
NAvalue(people_2016) <- -9999
cv_2016 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2016/cv_2016_ei_reclass.shp")
cv_2016$cpu<- as.factor(cv_2016$cpu)
cv_2016$eic_hig <- 0
cv_2016$eic_hig[cv_2016$eic_noh == '4'] <- 1 
names(cv_2016)
cv_2016 <- cv_2016[,c(1,12,27:31)]
target <- c('1') # select only the rows where EI with no habitat = 4
cv_2016_eic_hig <- cv_2016[cv_2016$eic_hig %in% target,] 
subtarget <- c('1','2','3') # select only the rows where the EI change from the high risk class
cv_2016_eic_hig <- cv_2016_eic_hig[cv_2016_eic_hig$risk_dlt %in% subtarget,]
cv_2016_eic_hig$ppl_raw <- raster::extract(people_2016, cv_2016_eic_hig, method='simple')
cv_2016_eic_hig$ppl <- cv_2016_eic_hig$ppl_raw*25
cv_2016_eic_hig_sp <- as(cv_2016_eic_hig, "Spatial")
class(cv_2016_eic_hig_sp)
writeOGR(obj=cv_2016_eic_hig_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2016", layer="cv_2016_ei_reclass_delta_high_w_people", driver="ESRI Shapefile", overwrite_layer =  T)
```

Do the same for 2020
```{r Count the number of people changing EI class high in 2020}
people_2020 <- raster("E:/GreenFin/02_cv_model/cv_inputs/bz_ppp_2020_2km_mean.tif")
NAvalue(people_2020) <- -9999
cv_2020 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2020/cv_2020_ei_reclass.shp")
cv_2020$cpu<- as.factor(cv_2020$cpu)
cv_2020$eic_hig <- 0
cv_2020$eic_hig[cv_2016$eic_noh == '4'] <- 1 
names(cv_2020)
cv_2020 <- cv_2020[,c(1,12,27:30)]
target <- c('1') # select only the rows where EI with no habitat = 4
cv_2020_eic_hig <- cv_2020[cv_2020$eic_hig %in% target,] 
subtarget <- c('1','2','3') # select only the rows where the EI change from the high risk class
cv_2020_eic_hig <- cv_2020_eic_hig[cv_2020_eic_hig$risk_dlt %in% subtarget,]
cv_2020_eic_hig$ppl_raw <- raster::extract(people_2020, cv_2020_eic_hig, method='simple')
cv_2020_eic_hig$ppl <- cv_2020_eic_hig$ppl_raw*25
cv_2020_eic_hig_sp <- as(cv_2020_eic_hig, "Spatial")
class(cv_2020_eic_hig_sp)
writeOGR(obj=cv_2020_eic_hig_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2020", layer="cv_2020_ei_reclass_delta_high_w_people", driver="ESRI Shapefile", overwrite_layer =  T)
```

And 2025
```{r Count the number of people changing EI class high in 2025}
people_2020 <- raster("E:/GreenFin/02_cv_model/cv_inputs/bz_ppp_2020_2km_mean.tif")
NAvalue(people_2020) <- -9999
cv_2025 <- st_read("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2025/cv_2025_ei_reclass.shp")
names(cv_2025)
cv_2025$eic_hig <- 0
cv_2025$eic_hig[cv_2016$eic_noh == '4'] <- 1 
names(cv_2025)
cv_2025 <- cv_2025[,c(1,12,27:30)]
target <- c('1') # select only the rows where EI with no habitat = 4
cv_2025_eic_hig <- cv_2025[cv_2025$eic_hig %in% target,] 
subtarget <- c('1','2','3') # select only the rows where the EI change from the high risk class
cv_2025_eic_hig <- cv_2025_eic_hig[cv_2025_eic_hig$risk_dlt %in% subtarget,]
cv_2025_eic_hig$ppl_raw <- raster::extract(people_2020, cv_2025_eic_hig, method='simple')
cv_2025_eic_hig$ppl <- cv_2025_eic_hig$ppl_raw*25
cv_2025_eic_hig_sp <- as(cv_2025_eic_hig, "Spatial")
class(cv_2025_eic_hig_sp)
writeOGR(obj=cv_2025_eic_hig_sp, dsn="E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/2025", layer="cv_2025_ei_reclass_delta_high_w_people", driver="ESRI Shapefile", overwrite_layer =  T)
```

Combine the values from people and km of shoreline at lesser risk from the 3 timelines into 1 to create summary tables for figures and metrics reporting
```{r Compute the number of km and people protected from high risk by habitats per CPU for each scenarios}
# 2016
cv_2016_risk_delta <- as.data.frame(cv_2016_eic_hig_sp)
cv_2016_risk_delta_km <- aggregate(shore_id ~ cpu, data = cv_2016_risk_delta, FUN = length)
cv_2016_risk_delta_km$km <- cv_2016_risk_delta_km$shore_id/4
cv_2016_risk_delta <- cv_2016_risk_delta[,c(2,8)] 
cv_2016_risk_delta_ppl <- aggregate(.~ cpu, data = cv_2016_risk_delta, FUN = sum)
cv_2016_risk_delta_ppl$ppl <- as.integer(cv_2016_risk_delta_ppl$ppl, digit=0)
cv_2016_risk_delta_by_cpu <- cbind(cv_2016_risk_delta_km,cv_2016_risk_delta_ppl)
cv_2016_risk_delta_by_cpu <- cv_2016_risk_delta_by_cpu[,-c(4)]
cv_2016_risk_delta_by_cpu$year <- "2016"
# 2020
cv_2020_risk_delta <- as.data.frame(cv_2020_eic_hig_sp)
cv_2020_risk_delta_km <- aggregate(shore_id ~ cpu, data = cv_2020_risk_delta, FUN = length)
cv_2020_risk_delta_km$km <- cv_2020_risk_delta_km$shore_id/4
cv_2020_risk_delta <- cv_2020_risk_delta[,c(2,7)] 
cv_2020_risk_delta_ppl <- aggregate(.~ cpu, data = cv_2020_risk_delta, FUN = sum)
cv_2020_risk_delta_ppl$ppl <- as.integer(cv_2020_risk_delta_ppl$ppl, digit=0)
cv_2020_risk_delta_by_cpu <- cbind(cv_2020_risk_delta_km,cv_2020_risk_delta_ppl)
cv_2020_risk_delta_by_cpu <- cv_2020_risk_delta_by_cpu[,-c(4)]
cv_2020_risk_delta_by_cpu$year <- "2020"
# 2025
cv_2025_risk_delta <- as.data.frame(cv_2025_eic_hig_sp)
cv_2025_risk_delta_km <- aggregate(shore_id ~ cpu, data = cv_2025_risk_delta, FUN = length)
cv_2025_risk_delta_km$km <- cv_2025_risk_delta_km$shore_id/4
cv_2025_risk_delta <- cv_2025_risk_delta[,c(2,7)] 
cv_2025_risk_delta_ppl <- aggregate(.~ cpu, data = cv_2025_risk_delta, FUN = sum)
cv_2025_risk_delta_ppl$ppl <- as.integer(cv_2025_risk_delta_ppl$ppl, digit=0)
cv_2025_risk_delta_by_cpu <- cbind(cv_2025_risk_delta_km,cv_2025_risk_delta_ppl)
cv_2025_risk_delta_by_cpu <- cv_2025_risk_delta_by_cpu[,-c(4)]
cv_2025_risk_delta_by_cpu$year <- "2025"
# combine
cv_risk_delta_by_cpu <- rbind(cv_2016_risk_delta_by_cpu, cv_2020_risk_delta_by_cpu, cv_2025_risk_delta_by_cpu)
write.csv(cv_risk_delta_by_cpu, paste0("E:/GreenFin/02_cv_model/cv_outputs/2016_habitats/", "cv_ei_delta_high_km_ppl_by_cpu.csv"), row.names = F)
```

# C/ Summarize the results into bar charts:

Create bar chart showing coastal risk reduction in in km due to habitat by CPU
```{r Build bar chart with km of shoreline protected by habitat at CPU scale}
cv_outputs <- read.csv("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats/cv_ei_delta_km_ppl_by_cpu.csv")
cpu_names <- read.csv("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats/cpu_name.csv")
cv_outputs <- cbind(cv_outputs, cpu_names) # add cpu names
cv_outputs <- cv_outputs[,-c(6:7)]
# add a column
cv_outputs$CV_model <- "Coastal Risk Exposure"
cv_outputs$CV_model <- factor(cv_outputs$CV_model,
                                   levels = c("Coastal Risk Exposure"))
cv_outputs$year <- factor(cv_outputs$year,
                           levels = c("2025", "2020", "2016"))
cv_outputs$cpuwname <- factor(cv_outputs$cpuwname,
                          levels = c("9-Southern Region","8-South Central Region","7-South Northern Region","6-Lighthouse Reef Atoll","5-Turneffe Atoll","4-Central Region","3-Caye Caulker","2-Ambergris Caye","1-Northern Region"))
year_cols <- c("deepskyblue", "darkorchid", "deeppink")
names(year_cols) <- c("2016", "2020", "2025")
ggbars <- ggplot(cv_outputs) +
  geom_bar(aes(x=cpuwname, y=km, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Shoreline Protected by Habitat", x = "Coastal Planning Units", y = "Shoreline at Lesser Risk (km)") +
  facet_wrap("CV_model") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 12, face="bold"), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text.x = element_text(angle = 45, hjust = 0.7, vjust = 0.8),
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
pdf(file.path("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats", paste("_barplot_cpu_shoreline_risk_mitigated_by_habitat_km.pdf")),
    width = 5, height = 5)
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
dev.off()
```

Create bar chart showing number of people protected by habitat at CPU scale
```{r Build bar chart with # of people protected by habitat at CPU scale}
cv_outputs <- read.csv("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats/cv_ei_delta_km_ppl_by_cpu.csv")
cpu_names <- read.csv("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats/cpu_name.csv")
cv_outputs <- cbind(cv_outputs, cpu_names) # add cpu names
cv_outputs <- cv_outputs[,-c(6:7)]
cv_outputs$CV_model <- "Coastal Risk Exposure"
cv_outputs$CV_model <- factor(cv_outputs$CV_model,
                                   levels = c("Coastal Risk Exposure"))
cv_outputs$year <- factor(cv_outputs$year,
                           levels = c("2025", "2020", "2016"))
cv_outputs$cpuwname <- factor(cv_outputs$cpuwname,
                          levels = c("9-Southern Region","8-South Central Region","7-South Northern Region","6-Lighthouse Reef Atoll","5-Turneffe Atoll","4-Central Region","3-Caye Caulker","2-Ambergris Caye","1-Northern Region"))
year_cols <- c("deepskyblue", "darkorchid", "deeppink")
names(year_cols) <- c("2016", "2020", "2025")
ggbars <- ggplot(cv_outputs) +
  geom_bar(aes(x=cpuwname, y=ppl, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "People Protected by Habitat", x = "Coastal Planning Units", y = "People at Lesser Risk (#)") +
  facet_wrap("CV_model") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 12, face="bold"), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text.x = element_text(angle = 45, hjust = 0.7, vjust = 0.8),
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
pdf(file.path("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats", paste("_barplot_cpu_shoreline_risk_mitigated_by_habitat_ppl.pdf")),
    width = 5, height = 5)
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
dev.off()
```

Create bar chart showing coastal risk reduction in in km due to habitat by CPU
```{r Build bar chart with km of shoreline protected from high risk by habitat at CPU scale}
cv_outputs <- read.csv("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats/cv_ei_delta_high_km_ppl_by_cpu.csv")
cpu_names <- read.csv("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats/cpu_name.csv")
cv_outputs <- cbind(cv_outputs, cpu_names) # add cpu names
cv_outputs <- cv_outputs[,-c(6:7)]
cv_outputs$CV_model <- "Coastal Risk Exposure"
cv_outputs$CV_model <- factor(cv_outputs$CV_model,
                                   levels = c("Coastal Risk Exposure"))
cv_outputs$year <- factor(cv_outputs$year,
                           levels = c("2025", "2020", "2016"))
cv_outputs$cpuwname <- factor(cv_outputs$cpuwname,
                          levels = c("9-Southern Region","8-South Central Region","7-South Northern Region","6-Lighthouse Reef Atoll","5-Turneffe Atoll","4-Central Region","3-Caye Caulker","2-Ambergris Caye","1-Northern Region"))
year_cols <- c("deepskyblue", "darkorchid", "deeppink")
names(year_cols) <- c("2016", "2020", "2025")
ggbars <- ggplot(cv_outputs) +
  geom_bar(aes(x=cpuwname, y=km, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "Shoreline Protected by Habitat", x = "Coastal Planning Units", y = "Shoreline at Lesser Risk (km)") +
  facet_wrap("CV_model") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 12, face="bold"), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text.x = element_text(angle = 45, hjust = 0.7, vjust = 0.8),
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
pdf(file.path("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats", paste("_barplot_cpu_shoreline_high_risk_mitigated_by_habitat_km.pdf")),
    width = 5, height = 5)
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
dev.off()
```

Create bar chart showing number of poeple protected by habitat at CPU scale
```{r Build bar chart with # of people protected from high risk by habitat at CPU scale}
cv_outputs <- read.csv("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats/cv_ei_delta_high_km_ppl_by_cpu.csv")
cpu_names <- read.csv("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats/cpu_name.csv")
cv_outputs <- cbind(cv_outputs, cpu_names) # add cpu names
cv_outputs <- cv_outputs[,-c(6:7)]
cv_outputs$CV_model <- "Coastal Risk Exposure"
cv_outputs$CV_model <- factor(cv_outputs$CV_model,
                                   levels = c("Coastal Risk Exposure"))
cv_outputs$year <- factor(cv_outputs$year,
                           levels = c("2025", "2020", "2016"))
cv_outputs$cpuwname <- factor(cv_outputs$cpuwname,
                          levels = c("9-Southern Region","8-South Central Region","7-South Northern Region","6-Lighthouse Reef Atoll","5-Turneffe Atoll","4-Central Region","3-Caye Caulker","2-Ambergris Caye","1-Northern Region"))
year_cols <- c("deepskyblue", "darkorchid", "deeppink")
names(year_cols) <- c("2016", "2020", "2025")
ggbars <- ggplot(cv_outputs) +
  geom_bar(aes(x=cpuwname, y=ppl, fill=year), position="dodge", stat="identity") +
  scale_fill_manual(values=year_cols) +
  labs(title = "People Protected by Habitat", x = "Coastal Planning Units", y = "People at Lesser Risk (#)") +
  facet_wrap("CV_model") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 12, face="bold"), 
        axis.title.y = element_text(size = 12, face="bold"), 
        axis.text.x = element_text(angle = 45, hjust = 0.7, vjust = 0.8),
        axis.text = element_text(size = 12, color = "black"),
        strip.text.x = element_text(size = 12),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=12),
        legend.position="bottom")
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
pdf(file.path("E:/Greenfin/02_cv_model/cv_outputs/2016_habitats", paste("_barplot_cpu_shoreline_high_risk_mitigated_by_habitat_ppl.pdf")),
    width = 5, height = 5)
plot_grid(ggbars + coord_flip() + scale_y_continuous(labels = scales::comma))
dev.off()
```
